---
title: "Supplemental Fitness models output"
author: "Malika Ihle"
date: "April 2, 2018"
output: pdf_document
---

```{r, echo=FALSE, results="hide", message=FALSE, warnings=FALSE, include =FALSE}
source('C:\\Users\\malika.ihle\\Documents\\_Malika_Sheffield\\_CURRENT BACKUP\\stats&data_extraction\\_ProvisioningDataCombination\\Coordination_DataAnalyses.R')
```


## Variable names and description:
**_A_**: count of alternated visits  
**_BreedingYear_**: year during which the brood was raised  
**_BroodRef_**: unique identifier for broods  
**_ChickAgeCat_**: the chick age as a categorical variable (chicks are routinely recorded at 6 and 10 days old, recordings deviating from that were pooled according to whether they were inferior, or superior (or equal) to 10)  
**_DadAge_**:age of the social male parent (in years)  
**_dam_**: genetic female parent of a chick  
**_DVDInfoChickNb_**: the best estimate of the number of chicks at time of recording  
**_DVDRef_**: nest watch unique identifier  
**_FwillDivorce_**: Whether or not (1/0) female repaired while her previous partner was still alive, after a specific recorded brood she had with that initial partner 
**_GenPairID_**: combination of the dan and sire IDs  
**_HatchingDayAfter0401_**: the numbers of day after the first of April of that year  
**_MeanFVisit1RateH_**: for males, the partner’s provisioning rate in number of visits per hour  
**_MeanLogAdev_**: logarithm of the deviation in alternation [log ((A observed+0.5) / (A random+0.5)], averaged accross all nest watch for that brood  
**_MeanLogSdev_**: logarithm of the deviation in synchrony, averaged accross all nest watch for that brood  
**_MeanMVisit1RateH_**: for females, the partner’s provisioning rate in number of visits per hour  
**_MeanTotalProRate_**: the average total provisioning rate for that brood in number of visits per hour   
**_MixedBroodYN_**: whether or not (1/0) the brood contained cross-fostered chicks  
**_MPriorResidence_**: whether or not (1/0) a male had nested in this nest box prior to the breeding attempt recorded  
**_MumAge_**:age of the social female parent (in years)  
**_MwillDivorce_**: Whether or not (1/0) male repaired while his previous partner was still alive, after a specific recorded brood he had with that initial partner  
**_NbHatched_**: number of chicks that hatched in that brood  
**_NBRinged_**:number of chicks ringed in that brood  
**_PairBroodNb_**: the number of brood a pair already reared together (successfully or unsuccessfully, including the brood of interest)  
**_PairID_**: combination of the social parents IDs  
**_PairIDYear_**: combination of the Pair ID and the breeding year  
**_ParentsAge_**: average of both parents age (in this population, pairs are assortatively mated for age, correlation between male and female age is r= 0.34, p <0.0001)   
**_RearingBrood_**:the brood where chicks were reared (foster brood for cross-fostered chicks)  
**_RelTimeHrs_**: the time, relative to sunrise, at which the video was taken  
**_ResMassTarsus_perChick_**: residuals of the regression of chick mass over its tarsus length  
**_rowID_**: observation level ID  
**_S_**: count of synchroneous visits  
**_sdResMassTarsus_**: standard deviation of the residuals of the regression of chick mass over its tarsus length  
**_sire_**: genetic male parent of a chick  
**_SocialDadID_**: unique idenifier for male parent observed caring for a brood  
**_SocialMumID_**: unique idenifier for female parent observed caring for a brood  
**_TotalProRate_**: the total number of visits provided by both partners divided by the entire duration of the nest watch in hours   
**_Type_**: the type of data (observed ("z_Obsv") or randomized ("Exp")  
**_VisitRateDifference_**: the difference in visit rate per hour between the partner  



## Fitness correlates

### Chick Survival

```{r, echo=FALSE}
summary(modChickSurvival) 
```

### Chick Mass

```{r, echo=FALSE}
summary(modChickMass) 
```

### Variance in Chick Body Condition (residuals of mass on tarsus)

```{r, echo=FALSE}
summary(modChickMassVariance)
```

### Range in chick mass

```{r, echo=FALSE}
summary(modChickMassRange)
```

## Divorce correlates

### Male

```{r, echo=FALSE}
summary(mod_MaleDivorce) 
```
### Female

```{r, echo=FALSE}
summary(mod_FemaleDivorce)
```



