---
title: "Supplemental Text 2"
author: "Malika Ihle"
date: "April 2, 2018"
output: pdf_document
classoption: landscape
---

```{r, echo=FALSE, results="hide", message=FALSE, warnings=FALSE, include =FALSE}
source('C:\\Users\\malika.ihle\\Documents\\_Malika_Sheffield\\_CURRENT BACKUP\\stats&data_extraction\\_ProvisioningDataCombination\\Coordination_DataAnalyses.R')
```



## Variable names and description:
**_A_**: count of alternated visits  
**_BreedingYear_**: year during which the brood was raised  
**_BroodRef_**: unique identifier for broods  
**_ChickAgeCat_**: the chick age as a categorical variable (chicks are routinely recorded at 6 and 10 days old, recordings deviating from that were pooled according to whether they were inferior, or superior (or equal) to 10)  
**_DVDInfoChickNb_**: the best estimate of the number of chicks at time of recording  
**_DVDRef_**: nest watch unique identifier  
**_HatchingDayAfter0401_**: the numbers of day after the first of April of that year  
**_MPriorResidence_**: whether or not (1/0) a male had nested in this nest box prior to the breeding attempt recorded  
**_PairBroodNb_**: the number of brood a pair already reared together (successfully or unsuccessfully, including the brood of interest)  
**_PairID_**: combination of the social parents IDs  
**_PairIDYear_**: combination of the Pair ID and the breeding year  
**_ParentsAge_**: average of both parents age (in this population, pairs are assortatively mated for age, correlation between male and female age is r= 0.34, p <0.0001)   
**_RelTimeHrs_**: the time, relative to sunrise, at which the video was taken  
**_rowID_**: observation level ID  
**_S_**: count of synchroneous visits  
**_SocialDadID_**: unique idenifier for male parent observed caring for a brood  
**_SocialMumID_**: unique idenifier for female parent observed caring for a brood  
**_TotalProRate_**: the total number of visits provided by both partners divided by the entire duration of the nest watch in hours   
**_Type_**: the type of data (observed ("z_Obsv") or randomized ("Exp")  
**_VisitRateDifference_**: the difference in visit rate per hour between the partner  

*****
## Predictors of coordination

### Alternation

```{r set-options, echo=FALSE}
options(width=120)
summary(modA)
```
*****


### Synchrony

```{r, echo=FALSE}
summary(modS)
```


